---
title: "Practicum Draft - 01-25-15 0800AM"
output: html_document
---

```{r, results="asis", echo=FALSE, message=FALSE}
 source('../RCode/Download and Clean PT Data.R')
 source('../RCode/Find Duplicate IDs.R')
 source('../RCode/PT Analysis.R')
 tablecount = 0
 figurecount = 0
```

Document was last updated on `r Sys.time()`.

*** 

# How is private tutoring framed? 
## A mixed-methods analysis of the private tutoring literature

## Abstract <!-- 600 words -->

## Introduction <!-- 1-2 paragraphs -->

### Overview

In homes, schoolrooms and tutoring centers all around the world, students end their official school day and begin a second round of studies. 
Almost always for a fee, these students take extra lessons to better prepare themselves for exams, QQQ, or simply because that is what is expected of them. In Cambodia a students return to school after lunch for a second math class. 
In the United States, students are bussed to tutoring centers where they are prepared for their end of the year tests in math and language arts. 
In Japan, students pack into crowded juku centers to prepare for national college-entrance exams.

These are all well known examples of private tutoring, but what of other forms of supplementary education? 
Art lessons, cultural courses, and language classes all take place outside the regular school structure, so does the literature consider them to be private tutoring? 
Similarly, does a fee need to be charged before we call something private tutoring or shadow education? How does the literature describe private tutoring? 
As a corrupt practice that preys on disadvantaged students, or simply the natural workings of the educational market? 
Do people who pursue private tutoring feel the mainstream education system has somehow failed?

We can begin answering these questions by looking at how private tutoring is framed within the various publications. 
A complex phenomenon, private tutoring alternatively framed as corruption among teachers, a way of promoting social cohesion, or simply a way to cover material needed for national exams.

In homes, schoolrooms and tutoring centers all around the world, students end their official school day and begin a second round of studies. 
Almost always for a fee, these students take extra lessons to better prepare themselves for exams, QQQ, or simply because that is what is expected of them. 
In Cambodia a students return to school after lunch for a second math class. 
In the United States students are bussed to tutoring centers where they are prepared for their end of the year tests in math and language arts. 
In Japan students pack into crowded juku centers to prepare for national college-entrance exams.

These are all well known examples of private tutoring, but what of other forms of supplementary education? 
Art lessons, cultural courses, and language classes all take place outside the regular school structure, so does the literature consider them to be private tutoring? 
Similarly, does a fee need to be charged before we call something private tutoring or shadow education? How does the literature describe private tutoring? 
As a corrupt practice that preys on disadvantaged students, or simply the natural workings of the educational market? 
Do people who pursue private tutoring feel the mainstream education system has somehow failed?

We can begin answering these questions by looking at how private tutoring is framed within the various publications. 
A complex phenomenon, private tutoring alternatively framed as corruption among teachers, a way of promoting social cohesion, or simply a way to cover material needed for national exams.

### Relevant Theories and Past Research

#### Critical Discourse Analysis

#### Private tutoring as a field of study. 


### The Present Research

In our literature analysis we wish to address the following questions:

*  How do authors frame private tutoring in comparative and international education publications?
*  Do authors frame private tutoring differently in different geographical contexts?
*  Has the way the literature frames private tutoring changed over time?
*  Do quantitative and qualitative researchers frame private tutoring differently?
*  Are there differences in the way private tutoring is framed between papers with take a single-case versus a comparative approach.

## Methods

### Sample

The process began with an exhaustive search for all Chinese-language and English-language articles, books and book chapters, dissertations, and reports related to private tutoring, supplementary education, cram schools, and non-state provision of education. 
Publications were selected using two criteria. 
One, the focus was on private tutoring as an educational phenomenon. Publications briefly mentioning private tutoring or describing techniques to provide private tutoring were removed from the pool. 
Two, studies were written prior to March 31, 2014. 
Conference papers where not included in the final analysis. 
This search resulted in 286 publications. 
This paper will focus just on English-language publications, of which there were `r nrow(AllEnglish)`. Table `r tablecount+1 ` below shows the distribution among English-language publication types. 

```{r, results="asis", echo=FALSE, message=FALSE}
test <- data.frame(table(AllEnglish$PubType))
test[test==0] <- NA
test <- test[complete.cases(test),]
colnames(test) <- c("Publication Type","Freq.")
test <- arrange(test, -Freq.)
kable(test)
```

### Procedure 


