---
title: "Descriptives"
output:
  html_document:
    keep_md: yes
    toc: true
  pdf_document: default
---


```{r, results="asis", echo=FALSE, message=FALSE}
source('../RCode/Download and Clean PT Data.R')
source('../RCode/Find Duplicate IDs.R')
source('../RCode/PT Analysis.R')
```

### TOTAL NUMBER OF ARTICLES: `r nrow(Private)`
This number includes `r nrow(Dupes)` articles with duplicate ID numbers (`r nrow(ChDupes)` Chinese-language, `r nrow(EngDupes)` English-language). A full list of duplicate articles can be found [here](https://github.com/MikeRussellMcK/PTAnalysis/blob/master/Markdown%20and%20Output/Duplicates.md). 
Document was last updated on `r Sys.time()`.

Throughout this document the data are divided four ways:

* **All Entries or Private** - This dataset includes all rows in the database
* **All Asia** - Using the region column for reference, this dataset includes all articles with Central Asia, East Asia, South Asia, or Southeast Asia selected. Includes both Chinese- and English-language articles.
* **All Chinese** - Using the publication language column for reference, this dataset includes only those articles with Chinese-languge selected. All regions are included.
* **All English** - Using the publication language column for reference, this dataset includes only those articles with English-languge selected. All regions are included.

**Others** lists include entries from all articles. 

## Publication Details

### Type of Publication

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1="PubType"
YLim=350
PrivateGraph    <- AllDataPlot(Private, DataSource1, Private$PubType, Title1, YLim)
AllAsiaGraph    <- AllDataPlot(AllAsia, DataSource1, AllAsia$PubType, Title2, YLim)
AllChineseGraph <- AllDataPlot(AllChinese, DataSource1, AllChinese$PubType, Title3, YLim)
AllEnglishGraph <- AllDataPlot(AllEnglish, DataSource1, AllEnglish$PubType, Title4, YLim)
grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

### Publisher
```{r, results="asis", echo=FALSE, message=FALSE}
kable(data.frame(table(Private$Publisher)), format="html",  caption='Counts')
```

### Publication Year

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivatePubYearGrid
DataSource2=AllAsiaPubYearGrid
DataSource3=AllChinesePubYearGrid
DataSource4=AllEnglishPubYearGrid

YLim=120
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=4)
```

### Publication Language

```{r, results="asis", echo=FALSE, message=FALSE}

#DataSet1 <- PrivatePubLangLabel
GraphName1 <- "All Entries"

YLim=350
PrivateGraph <- CategoricalPlot(PrivatePubLangGrid, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(AllAsiaPubLangGrid, Title2, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, ncol=2)

```

### Type of Research

```{r, results="asis", echo=FALSE, message=FALSE}

DataSource1=PrivateResearchTypeGrid
YLim=225
PrivateGraph <- CategoricalPlot(PrivateResearchTypeGrid, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(AllAsiaResearchTypeGrid, Title2, YLim)
AllChineseGraph <- CategoricalPlot(AllChineseResearchTypeGrid, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(AllEnglishResearchTypeGrid, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=1)
```
    
#### Research Type Others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(ResearchTypeOther, row.names=FALSE)
```

## Subjects and Approach

### Country or Countries Studied

```{r, results="asis", echo=FALSE, message=FALSE}
kable(data.frame(table(Private$Country)), format="html",  caption='Counts')
```

### Region(s) Studied

```{r, results="asis", echo=FALSE, message=FALSE}
# kable(data.frame(table(Private$Region)), format="html",  caption='Raw Counts')
DataSource1=PrivateRegionGrid
DataSource2=AllAsiaRegionGrid
DataSource3=AllChineseRegionGrid
DataSource4=AllEnglishRegionGrid

YLim=275
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### Region(s) Others:

```{r, results="asis", echo=FALSE, message=FALSE}
# kable(RegionOther, row.names=FALSE)
```

### Levels of Education Discussed

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateEdLevelGrid
DataSource2=AllAsiaEdLevelGrid
DataSource3=AllChineseEdLevelGrid
DataSource4=AllEnglishEdLevelGrid

YLim=350
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### EdLevel Others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(EdLevelOther, row.names=FALSE)
```

### Research Approach

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateResearchApproachGrid
DataSource2=AllAsiaResearchApproachGrid
DataSource3=AllChineseResearchApproachGrid
DataSource4=AllEnglishResearchApproachGrid

YLim=350
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### ResearchApproach Others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(ResearchApproachOther, row.names=FALSE)
```

### Research Methods

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateResearchMethodsGrid
DataSource2=AllAsiaResearchMethodsGrid
DataSource3=AllChineseResearchMethodsGrid
DataSource4=AllEnglishResearchMethodsGrid

YLim=350
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

### Was data set used?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateWasDataGrid
DataSource2=AllAsiaWasDataGrid
DataSource3=AllChineseWasDataGrid
DataSource4=AllEnglishWasDataGrid

YLim=350
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### What data set was used?

```{r, results="asis", echo=FALSE, message=FALSE}
kable(data.frame(table(Private$WhatData)), format="html",  caption='Counts')
```

### Theoretical Framework

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateTheoryGrid
DataSource2=AllAsiaTheoryGrid
DataSource3=AllChineseTheoryGrid
DataSource4=AllEnglishTheoryGrid

YLim=350
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### Theory Others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(TheoryOther, format="html", row.names=FALSE)
```

### How is private tutoring framed in the publication?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateFramedGrid
DataSource2=AllAsiaFramedGrid
DataSource3=AllChineseFramedGrid
DataSource4=AllEnglishFramedGrid

YLim=325
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

#grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, nrow=4)
PrivateGraph
AllAsiaGraph
AllChineseGraph
AllEnglishGraph
```

#### Framed Others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(FramedOther, format="html", row.names=FALSE)
```

#### If previous answer was equity, then please define equity concern here:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(EquityConcernGrid, format="html",  row.names=FALSE)
```

### How is private tutoring viewed in the article?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateHowViewedGrid
DataSource2=AllAsiaHowViewedGrid
DataSource3=AllChineseHowViewedGrid
DataSource4=AllEnglishHowViewedGrid

YLim=300
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

### Data drawn from the following stakeholders:

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateStakeholdersGrid
DataSource2=AllAsiaStakeholdersGrid
DataSource3=AllChineseStakeholdersGrid
DataSource4=AllEnglishStakeholdersGrid

YLim=275
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### Stakeholder others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(StakeholdersOther, format="html", row.names=FALSE)
```

## Definition of Private Tutoring

### What is taught during private tutoring?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateWhatTaughtGrid
DataSource2=AllAsiaWhatTaughtGrid
DataSource3=AllChineseWhatTaughtGrid
DataSource4=AllEnglishWhatTaughtGrid

YLim=275
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### WhatTaught others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(WhatTaughtOther, format="html", row.names=FALSE)
```

### Where does private tutoring occur?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateWhereOccurGrid
DataSource2=AllAsiaWhereOccurGrid
DataSource3=AllChineseWhereOccurGrid
DataSource4=AllEnglishWhereOccurGrid

YLim=250
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=1)
```

#### WhereOccur others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(WhereOccurOther, format="html", row.names=FALSE)
```

### Who provides tutoring services?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateWhoProvidesGrid
DataSource2=AllAsiaWhoProvidesGrid
DataSource3=AllChineseWhoProvidesGrid
DataSource4=AllEnglishWhoProvidesGrid

YLim=275
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### WhoProvides others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(WhoProvidesOther, format="html", row.names=FALSE)
```

### Does the teacher charge for private tutoring?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1="DoesCharge"
YLim=350
PrivateGraph <- AllDataPlot(Private, DataSource1, Private$DoesCharge, Title1, YLim)
AllAsiaGraph <- AllDataPlot(AllAsia, DataSource1, AllAsia$DoesCharge, Title2, YLim)
AllChineseGraph <- AllDataPlot(AllChinese, DataSource1, AllChinese$DoesCharge, Title3, YLim)
AllEnglishGraph <- AllDataPlot(AllEnglish, DataSource1, AllEnglish$DoesCharge, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)

```

### How large are the tutoring classes?

```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1="ClassSize"
YLim=350
PrivateGraph <- AllDataPlot(Private, DataSource1, Private$ClassSize, Title1, YLim)
AllAsiaGraph <- AllDataPlot(AllAsia, DataSource1, AllAsia$ClassSize, Title2, YLim)
AllChineseGraph <- AllDataPlot(AllChinese, DataSource1, AllChinese$ClassSize, Title3, YLim)
AllEnglishGraph <- AllDataPlot(AllEnglish, DataSource1, AllEnglish$ClassSize, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

### How large is the tutoring operation?
```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateOperationSizeGrid
DataSource2=AllAsiaOperationSizeGrid
DataSource3=AllChineseOperationSizeGrid
DataSource4=AllEnglishOperationSizeGrid

YLim=300
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

grid.arrange(PrivateGraph, AllAsiaGraph, AllChineseGraph, AllEnglishGraph, ncol=2)
```

#### OperationSize others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(OperationSizeOther, format="html", row.names=FALSE)
```

### Why are students taking private tutoring?
```{r, results="asis", echo=FALSE, message=FALSE}
DataSource1=PrivateWhyTakingGrid
DataSource2=AllAsiaWhyTakingGrid
DataSource3=AllChineseWhyTakingGrid
DataSource4=AllEnglishWhyTakingGrid

YLim=350
PrivateGraph <- CategoricalPlot(DataSource1, Title1, YLim)
AllAsiaGraph <- CategoricalPlot(DataSource2, Title2, YLim)
AllChineseGraph <- CategoricalPlot(DataSource3, Title3, YLim)
AllEnglishGraph <- CategoricalPlot(DataSource4, Title4, YLim)

PrivateGraph
AllAsiaGraph
AllChineseGraph
AllEnglishGraph
```

#### WhyTaking others:

```{r, results="asis", echo=FALSE, message=FALSE}
kable(WhyTakingOther, format="html", row.names=FALSE)
```

## Additional Details
```{r, results="asis", echo=FALSE, message=FALSE}
kable(AddDetailsGrid, format="html",  row.names=FALSE)
```