---
title: "Private Tutoring Analysis"
output:
  html_document:
    keep_md: yes
  pdf_document: default
---


```{r, results="asis", echo=FALSE, message=FALSE}
source('../RCode/Download and Clean PT Data.R')
source('../RCode/PT Analysis.R')
```

### Type of Publication



### Research Type

#### All sources

**Research Type Counts:**

```{r, results="asis", echo=FALSE, message=FALSE}
kable(data.frame(colSums(ResearchTypeGrid)))
```

**Research Type Percentages:**

```{r, results="asis", echo=FALSE, message=FALSE}
kable(prop.table(data.frame(colSums(ResearchTypeGrid))))
```

**Research Type Others:** 

```{r, results="asis", echo=FALSE, message=FALSE}
kable(ResearchTypeOther, row.names=FALSE)
```

#### Asian region only

### Language Counts

**Number of Chinese-language articles:** `r sum(grepl("Chinese",Private$PubLang))` (`r paste(round(sum(grepl("Chinese",Private$PubLang))/nrow(Private), digits=4)*100, "%")`)  
**Number of English-language articles:** `r sum(grepl("English",Private$PubLang))` (`r paste(round(sum(grepl("English",Private$PubLang))/nrow(Private), digits=4)*100, "%")`)