---
title: "Relationships for All Articles"
output:
  html_document:
    keep_md: yes
    toc: true
  pdf_document: default
---

```{r, results="asis", echo=FALSE, message=FALSE}
source('../RCode/Download and Clean PT Data.R')
source('../RCode/PT Analysis.R')
```

# _Region by year group_ for all entries in the database:

### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByYear<-data.frame(Private$YearGroup, PrivateRegionGrid) #Grid vs column
RegionByYear2 <- melt(RegionByYear, id=c("Private.YearGroup"))
RegionByYear3<-RegionByYear2[!(RegionByYear2$value=="FALSE"),]
names(RegionByYear3) <- c("YearGroup","Region","value")
ggplot(RegionByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByYear3$YearGroup, RegionByYear3$Region))
```

# _Region by publication type_: 

### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByPubType <- data.frame(Private$PubType, PrivateRegionGrid) #Grid vs column
RegionByPubType2 <- melt(RegionByPubType, id=c("Private.PubType"))
RegionByPubType3<-RegionByPubType2[!(RegionByPubType2$value=="FALSE"),]
names(RegionByPubType3) <- c("PubType","Region","value")
ggplot(RegionByPubType3, aes(PubType))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByPubType3$PubType, RegionByPubType3$Region))
```

# _Publication type by year group_ for all entries in the database:

### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ggplot(Private, aes(YearGroup))+geom_bar()+facet_wrap(~PubType)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(Private$YearGroup, Private$PubType))
```

# _Research type by region_ for all entries in the database

### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByResearchType <- data.frame(PrivateResearchTypeGrid, PrivateRegionGrid) # Double-grid
RegionByResearchType2 <- melt(RegionByResearchType, id=c("Original.emperical.research", "Review.of.other.research", "Policy.analysis"))
RegionByResearchType3<-RegionByResearchType2[!(RegionByResearchType2$value=="FALSE"),]
names(RegionByResearchType3) <- c("Original emperical", "Review of other", "Policy analysis","Region","value")
RegionByResearchType3 <- melt(RegionByResearchType3, id=c("Region"))
RegionByResearchType3<-RegionByResearchType3[!(RegionByResearchType3$value=="FALSE"),]
names(RegionByResearchType3) <- c("Region","ResearchType", "value")
RegionByResearchType3<-RegionByResearchType3[!(RegionByResearchType3$ResearchType=="value"),]
ggplot(RegionByResearchType3, aes(ResearchType))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByResearchType3$Region, RegionByResearchType3$ResearchType))
```

# _Research type by year group_ for all entries in the database

### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchTypeByYear<-data.frame(Private$YearGroup, PrivateResearchTypeGrid) #Grid vs column
ResearchTypeByYear2 <- melt(ResearchTypeByYear, id=c("Private.YearGroup"))
ResearchTypeByYear3<-ResearchTypeByYear2[!(ResearchTypeByYear2$value=="FALSE"),] 
names(ResearchTypeByYear3) <- c("YearGroup","ResearchType","value")
ggplot(ResearchTypeByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~ResearchType)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchTypeByYear3$YearGroup, ResearchTypeByYear3$ResearchType))
```

# _Ed levels by region_ 

### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByEdLevel <- data.frame(PrivateEdLevelGrid, PrivateRegionGrid) # Double-grid
RegionByEdLevel2 <- melt(RegionByEdLevel, id=c("Pre.primary","Primary","Secondary","Tertiary"))
RegionByEdLevel3<-RegionByEdLevel2[!(RegionByEdLevel2$value=="FALSE"),]
names(RegionByEdLevel3) <- c("Pre-primary","Primary","Secondary","Tertiary","Region","value")
RegionByEdLevel3 <- melt(RegionByEdLevel3, id=c("Region"))
RegionByEdLevel3<-RegionByEdLevel3[!(RegionByEdLevel3$value=="FALSE"),]
names(RegionByEdLevel3) <- c("Region","EdLevel", "value")
RegionByEdLevel3<-RegionByEdLevel3[!(RegionByEdLevel3$EdLevel=="value"),]
ggplot(RegionByEdLevel3, aes(EdLevel))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByEdLevel3$Region, RegionByEdLevel3$EdLevel))
```

# _Research approach by region_
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByResearchApproach <- data.frame(PrivateResearchApproachGrid, PrivateRegionGrid) # Double-grid
RegionByResearchApproach2 <- melt(RegionByResearchApproach, id=c("Single.country...case", "Comparative"))
RegionByResearchApproach3 <- RegionByResearchApproach2[!(RegionByResearchApproach2$value=="FALSE"),]
names(RegionByResearchApproach3) <- c("Single-country","Comparative", "Region","value")
RegionByResearchApproach3 <- melt(RegionByResearchApproach3, id=c("Region"))
RegionByResearchApproach3<-RegionByResearchApproach3[!(RegionByResearchApproach3$value=="FALSE"),]
names(RegionByResearchApproach3) <- c("Region","ResearchApproach", "value")
RegionByResearchApproach3<-RegionByResearchApproach3[!(RegionByResearchApproach3$ResearchApproach=="value"),]
ggplot(RegionByResearchApproach3, aes(ResearchApproach))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByResearchApproach3$Region, RegionByResearchApproach3$ResearchApproach))
```

# Research approach by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchApproachByYear<-data.frame(Private$YearGroup, PrivateResearchApproachGrid) #Grid vs column
ResearchApproachByYear2 <- melt(ResearchApproachByYear, id=c("Private.YearGroup"))
ResearchApproachByYear3<-ResearchApproachByYear2[!(ResearchApproachByYear2$value=="FALSE"),]
names(ResearchApproachByYear3) <- c("YearGroup","ResearchApproach","value")
ggplot(ResearchApproachByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~ResearchApproach)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchApproachByYear3$YearGroup, ResearchApproachByYear3$ResearchApproach))
```

# Research methods by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ggplot(Private, aes(YearGroup))+geom_bar()+facet_wrap(~ResearchMethods)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(Private$YearGroup, Private$ResearchMethods))
```

# Research methods by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByResearchMethods <- data.frame(Private$ResearchMethods, PrivateRegionGrid)
RegionByResearchMethods2 <- melt(RegionByResearchMethods, id=c("Private.ResearchMethods"))
RegionByResearchMethods3 <- RegionByResearchMethods2[!(RegionByResearchMethods2$value=="FALSE"),]
names(RegionByResearchMethods3) <- c("ResearchMethods","Region","value")
ggplot(RegionByResearchMethods3, aes(ResearchMethods))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByResearchMethods3$Region, RegionByResearchMethods3$ResearchMethods))
```

# Research methods by year group
### Graph for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ggplot(Private, aes(YearGroup))+geom_bar()+facet_wrap(~ResearchMethods)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(Private$YearGroup, Private$ResearchMethods))
```

# Research methods by publication type
### Graph for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ggplot(Private, aes(PubType))+geom_bar()+facet_wrap(~ResearchMethods)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(Private$PubType, Private$ResearchMethods))
```

# Theoreortical framework by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByTheory <- data.frame(PrivateTheoryGrid, PrivateRegionGrid) # Double-grid
RegionByTheory2 <- melt(RegionByTheory, id=c("Social.Capital","Human.Capital", "Cultural.Capital", "World.Culture", "Human.Rights","Critical.Theory","Political.Theory","None.or.Unclear.to.us"))
RegionByTheory3 <- RegionByTheory2[!(RegionByTheory2$value=="FALSE"),]
names(RegionByTheory3) <- c("Social Capital","Human Capital", "Cultural Capital", "World Culture", "Human Rights","Critical Theory","Political Theory","None or Unclear to us", "Region", "value")
RegionByTheory3 <- melt(RegionByTheory3, id=c("Region"))
RegionByTheory3<-RegionByTheory3[!(RegionByTheory3$value=="FALSE"),]
names(RegionByTheory3) <- c("Region","Theory", "value")
RegionByTheory3<-RegionByTheory3[!(RegionByTheory3$Theory=="value"),]
ggplot(RegionByTheory3, aes(Theory))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByTheory3$Theory, RegionByTheory3$Region))
```

# Theoreortical framework by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
TheoryByYear<-data.frame(Private$YearGroup, PrivateTheoryGrid) #Grid vs column
TheoryByYear2 <- melt(TheoryByYear, id=c("Private.YearGroup"))
TheoryByYear3<-TheoryByYear2[!(TheoryByYear2$value=="FALSE"),] 
names(TheoryByYear3) <- c("YearGroup","Theory","value")
ggplot(TheoryByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Theory)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(TheoryByYear3$YearGroup, TheoryByYear3$Theory))
```

# Theoretical framework by research method
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchMethodsByTheory <- data.frame(PrivateTheoryGrid, PrivateResearchMethodsGrid) # Double-grid
ResearchMethodsByTheory2 <- melt(ResearchMethodsByTheory, id=c("Social.Capital","Human.Capital", "Cultural.Capital", "World.Culture", "Human.Rights","Critical.Theory","Political.Theory","None.or.Unclear.to.us"))
ResearchMethodsByTheory3 <- ResearchMethodsByTheory2[!(ResearchMethodsByTheory2$value=="FALSE"),]
names(ResearchMethodsByTheory3) <- c("Social Capital","Human Capital", "Cultural Capital", "World Culture", "Human Rights","Critical Theory","Political Theory","None or Unclear to us", "ResearchMethods", "value")
ResearchMethodsByTheory3 <- melt(ResearchMethodsByTheory3, id=c("ResearchMethods"))
ResearchMethodsByTheory3<-ResearchMethodsByTheory3[!(ResearchMethodsByTheory3$value=="FALSE"),]
names(ResearchMethodsByTheory3) <- c("ResearchMethods","Theory", "value")
ResearchMethodsByTheory3<-ResearchMethodsByTheory3[!(ResearchMethodsByTheory3$Theory=="value"),]
ggplot(ResearchMethodsByTheory3, aes(Theory))+geom_bar()+facet_wrap(~ResearchMethods)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchMethodsByTheory3$Theory, ResearchMethodsByTheory3$ResearchMethods))
```

# Theoretical framework by research approach
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchApproachByTheory <- data.frame(PrivateTheoryGrid, PrivateResearchApproachGrid) # Double-grid
ResearchApproachByTheory2 <- melt(ResearchApproachByTheory, id=c("Social.Capital","Human.Capital", "Cultural.Capital", "World.Culture", "Human.Rights","Critical.Theory","Political.Theory","None.or.Unclear.to.us"))
ResearchApproachByTheory3 <- ResearchApproachByTheory2[!(ResearchApproachByTheory2$value=="FALSE"),]
names(ResearchApproachByTheory3) <- c("Social Capital","Human Capital", "Cultural Capital", "World Culture", "Human Rights","Critical Theory","Political Theory","None or Unclear to us", "ResearchApproach", "value")
ResearchApproachByTheory3 <- melt(ResearchApproachByTheory3, id=c("ResearchApproach"))
ResearchApproachByTheory3<-ResearchApproachByTheory3[!(ResearchApproachByTheory3$value=="FALSE"),]
names(ResearchApproachByTheory3) <- c("ResearchApproach","Theory", "value")
ResearchApproachByTheory3<-ResearchApproachByTheory3[!(ResearchApproachByTheory3$Theory=="value"),]
ggplot(ResearchApproachByTheory3, aes(Theory))+geom_bar()+facet_wrap(~ResearchApproach)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchApproachByTheory3$Theory, ResearchApproachByTheory3$ResearchApproach))
```

# Framing by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByFramed <- data.frame(PrivateFramedGrid, PrivateRegionGrid) # Double-grid
RegionByFramed2 <- melt(RegionByFramed, id=c("Related.to.curriculum.coverage...ed..quality...exam.prep","Corruption", "Equity", "Supply...Demand...Economic.Efficiency", "X.Social.Cohesion","Global.Trend","Household.Expenditures"))
RegionByFramed3 <- RegionByFramed2[!(RegionByFramed2$value=="FALSE"),]
names(RegionByFramed3) <- c("Exam Prep", "Corruption", "Equity", "Economic", "Social Cohesion", "Global Trend", "Household", "Region", "value")
RegionByFramed3 <- melt(RegionByFramed3, id=c("Region"))
RegionByFramed3<-RegionByFramed3[!(RegionByFramed3$value=="FALSE"),]
names(RegionByFramed3) <- c("Region","Framed", "value")
RegionByFramed3<-RegionByFramed3[!(RegionByFramed3$Framed=="value"),]
ggplot(RegionByFramed3, aes(Framed))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByFramed3$Framed, RegionByFramed3$Region))
```

# Framing by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
FramedByYear<-data.frame(Private$YearGroup, PrivateFramedGrid) #Grid vs column
FramedByYear2 <- melt(FramedByYear, id=c("Private.YearGroup"))
FramedByYear3<-FramedByYear2[!(FramedByYear2$value=="FALSE"),] 
names(FramedByYear3) <- c("YearGroup","Framed","value")
ggplot(FramedByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Framed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(FramedByYear3$YearGroup, FramedByYear3$Framed))
```

# Framed by research method
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchMethodsByFramed <- data.frame(PrivateFramedGrid, PrivateResearchMethodsGrid) # Double-grid
ResearchMethodsByFramed2 <- melt(ResearchMethodsByFramed, id=c("Related.to.curriculum.coverage...ed..quality...exam.prep","Corruption", "Equity", "Supply...Demand...Economic.Efficiency", "X.Social.Cohesion","Global.Trend","Household.Expenditures"))
ResearchMethodsByFramed3 <- ResearchMethodsByFramed2[!(ResearchMethodsByFramed2$value=="FALSE"),]
names(ResearchMethodsByFramed3) <- c("Exam Prep", "Corruption", "Equity", "Economic", "Social Cohesion", "Global Trend", "Household", "ResearchMethods", "value")
ResearchMethodsByFramed3 <- melt(ResearchMethodsByFramed3, id=c("ResearchMethods"))
ResearchMethodsByFramed3<-ResearchMethodsByFramed3[!(ResearchMethodsByFramed3$value=="FALSE"),]
names(ResearchMethodsByFramed3) <- c("ResearchMethods","Framed", "value")
ResearchMethodsByFramed3<-ResearchMethodsByFramed3[!(ResearchMethodsByFramed3$Framed=="value"),]
ggplot(ResearchMethodsByFramed3, aes(ResearchMethods))+geom_bar()+facet_wrap(~Framed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchMethodsByFramed3$Framed, ResearchMethodsByFramed3$ResearchMethods))
```

# Framed by research approach
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchApproachByFramed <- data.frame(PrivateFramedGrid, PrivateResearchApproachGrid) # Double-grid
ResearchApproachByFramed2 <- melt(ResearchApproachByFramed, id=c("Related.to.curriculum.coverage...ed..quality...exam.prep","Corruption", "Equity", "Supply...Demand...Economic.Efficiency", "X.Social.Cohesion","Global.Trend","Household.Expenditures"))
ResearchApproachByFramed3 <- ResearchApproachByFramed2[!(ResearchApproachByFramed2$value=="FALSE"),]
names(ResearchApproachByFramed3) <- c("Exam Prep", "Corruption", "Equity", "Economic", "Social Cohesion", "Global Trend", "Household", "ResearchApproach", "value")
ResearchApproachByFramed3 <- melt(ResearchApproachByFramed3, id=c("ResearchApproach"))
ResearchApproachByFramed3<-ResearchApproachByFramed3[!(ResearchApproachByFramed3$value=="FALSE"),]
names(ResearchApproachByFramed3) <- c("ResearchApproach","Framed", "value")
ResearchApproachByFramed3<-ResearchApproachByFramed3[!(ResearchApproachByFramed3$Framed=="value"),]
ggplot(ResearchApproachByFramed3, aes(ResearchApproach))+geom_bar()+facet_wrap(~Framed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchApproachByFramed3$Framed, ResearchApproachByFramed3$ResearchApproach))
```

# Framed by theory
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
FramedByTheory <- data.frame(PrivateTheoryGrid, PrivateFramedGrid) # Double-grid
FramedByTheory2 <- melt(FramedByTheory, id=c("Social.Capital","Human.Capital", "Cultural.Capital", "World.Culture", "Human.Rights","Critical.Theory","Political.Theory","None.or.Unclear.to.us"))
FramedByTheory3 <- FramedByTheory2[!(FramedByTheory2$value=="FALSE"),]
names(FramedByTheory3) <- c("Social Capital","Human Capital", "Cultural Capital", "World Culture", "Human Rights","Critical Theory","Political Theory","None or Unclear to us", "Framed", "value")
FramedByTheory3 <- melt(FramedByTheory3, id=c("Framed"))
FramedByTheory3<-FramedByTheory3[!(FramedByTheory3$value=="FALSE"),]
names(FramedByTheory3) <- c("Framed","Theory", "value")
FramedByTheory3<-FramedByTheory3[!(FramedByTheory3$Theory=="value"),]
ggplot(FramedByTheory3, aes(Theory))+geom_bar()+facet_wrap(~Framed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(FramedByTheory3$Framed, FramedByTheory3$Theory))
```

# How Viewed by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByHowViewed <- data.frame(PrivateHowViewedGrid, PrivateRegionGrid) # Double-grid
RegionByHowViewed2 <- melt(RegionByHowViewed, id=c("Raises.concerns","Discusses.benefits","Both","Neither"))
RegionByHowViewed3 <- RegionByHowViewed2[!(RegionByHowViewed2$value=="FALSE"),]
names(RegionByHowViewed3) <- c("Raises concerns","Discusses benefits","Both","Neither", "Region", "value")
RegionByHowViewed3 <- melt(RegionByHowViewed3, id=c("Region"))
RegionByHowViewed3<-RegionByHowViewed3[!(RegionByHowViewed3$value=="FALSE"),]
names(RegionByHowViewed3) <- c("Region","HowViewed", "value")
RegionByHowViewed3<-RegionByHowViewed3[!(RegionByHowViewed3$HowViewed=="value"),]
ggplot(RegionByHowViewed3, aes(HowViewed))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByHowViewed3$HowViewed, RegionByHowViewed3$Region))
```

# How Viewed by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
HowViewedByYear<-data.frame(Private$YearGroup, PrivateHowViewedGrid) #Grid vs column
HowViewedByYear2 <- melt(HowViewedByYear, id=c("Private.YearGroup"))
HowViewedByYear3<-HowViewedByYear2[!(HowViewedByYear2$value=="FALSE"),] 
names(HowViewedByYear3) <- c("YearGroup","HowViewed","value")
ggplot(HowViewedByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~HowViewed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(HowViewedByYear3$YearGroup, HowViewedByYear3$HowViewed))
```

# HowViewed by research method
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchMethodsByHowViewed <- data.frame(PrivateHowViewedGrid, PrivateResearchMethodsGrid) # Double-grid
ResearchMethodsByHowViewed2 <- melt(ResearchMethodsByHowViewed, id=c("Raises.concerns","Discusses.benefits","Both","Neither"))
ResearchMethodsByHowViewed3 <- ResearchMethodsByHowViewed2[!(ResearchMethodsByHowViewed2$value=="FALSE"),]
names(ResearchMethodsByHowViewed3) <- c("Raises concerns","Discusses benefits","Both","Neither", "ResearchMethods", "value")
ResearchMethodsByHowViewed3 <- melt(ResearchMethodsByHowViewed3, id=c("ResearchMethods"))
ResearchMethodsByHowViewed3<-ResearchMethodsByHowViewed3[!(ResearchMethodsByHowViewed3$value=="FALSE"),]
names(ResearchMethodsByHowViewed3) <- c("ResearchMethods","HowViewed", "value")
ResearchMethodsByHowViewed3<-ResearchMethodsByHowViewed3[!(ResearchMethodsByHowViewed3$HowViewed=="value"),]
ggplot(ResearchMethodsByHowViewed3, aes(ResearchMethods))+geom_bar()+facet_wrap(~HowViewed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchMethodsByHowViewed3$HowViewed, ResearchMethodsByHowViewed3$ResearchMethods))
```

# HowViewed by research approach
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchApproachByHowViewed <- data.frame(PrivateHowViewedGrid, PrivateResearchApproachGrid) # Double-grid
ResearchApproachByHowViewed2 <- melt(ResearchApproachByHowViewed, id=c("Raises.concerns","Discusses.benefits","Both","Neither"))
ResearchApproachByHowViewed3 <- ResearchApproachByHowViewed2[!(ResearchApproachByHowViewed2$value=="FALSE"),]
names(ResearchApproachByHowViewed3) <- c("Raises concerns","Discusses benefits","Both","Neither", "ResearchApproach", "value")
ResearchApproachByHowViewed3 <- melt(ResearchApproachByHowViewed3, id=c("ResearchApproach"))
ResearchApproachByHowViewed3<-ResearchApproachByHowViewed3[!(ResearchApproachByHowViewed3$value=="FALSE"),]
names(ResearchApproachByHowViewed3) <- c("ResearchApproach","HowViewed", "value")
ResearchApproachByHowViewed3<-ResearchApproachByHowViewed3[!(ResearchApproachByHowViewed3$HowViewed=="value"),]
ggplot(ResearchApproachByHowViewed3, aes(ResearchApproach))+geom_bar()+facet_wrap(~HowViewed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchApproachByHowViewed3$HowViewed, ResearchApproachByHowViewed3$ResearchApproach))
```

# HowViewed by theory
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
HowViewedByTheory <- data.frame(PrivateTheoryGrid, PrivateHowViewedGrid) # Double-grid
HowViewedByTheory2 <- melt(HowViewedByTheory, id=c("Social.Capital","Human.Capital", "Cultural.Capital", "World.Culture", "Human.Rights","Critical.Theory","Political.Theory","None.or.Unclear.to.us"))
HowViewedByTheory3 <- HowViewedByTheory2[!(HowViewedByTheory2$value=="FALSE"),]
names(HowViewedByTheory3) <- c("Social Capital","Human Capital", "Cultural Capital", "World Culture", "Human Rights","Critical Theory","Political Theory","None or Unclear to us", "HowViewed", "value")
HowViewedByTheory3 <- melt(HowViewedByTheory3, id=c("HowViewed"))
HowViewedByTheory3<-HowViewedByTheory3[!(HowViewedByTheory3$value=="FALSE"),]
names(HowViewedByTheory3) <- c("HowViewed","Theory", "value")
HowViewedByTheory3<-HowViewedByTheory3[!(HowViewedByTheory3$Theory=="value"),]
ggplot(HowViewedByTheory3, aes(HowViewed))+geom_bar()+facet_wrap(~Theory)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(HowViewedByTheory3$HowViewed, HowViewedByTheory3$Theory))
```

# How Viewed by Framed
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
FramedByHowViewed <- data.frame(PrivateHowViewedGrid, PrivateFramedGrid) # Double-grid
FramedByHowViewed2 <- melt(FramedByHowViewed, id=c("Raises.concerns","Discusses.benefits","Both","Neither"))
FramedByHowViewed3 <- FramedByHowViewed2[!(FramedByHowViewed2$value=="FALSE"),]
names(FramedByHowViewed3) <- c("Raises concerns","Discusses benefits","Both","Neither", "Framed", "value")
FramedByHowViewed3 <- melt(FramedByHowViewed3, id=c("Framed"))
FramedByHowViewed3<-FramedByHowViewed3[!(FramedByHowViewed3$value=="FALSE"),]
names(FramedByHowViewed3) <- c("Framed","HowViewed", "value")
FramedByHowViewed3<-FramedByHowViewed3[!(FramedByHowViewed3$HowViewed=="value"),]
ggplot(FramedByHowViewed3, aes(HowViewed))+geom_bar()+facet_wrap(~Framed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(FramedByHowViewed3$Framed, FramedByHowViewed3$HowViewed))
```

# Stakeholders by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByStakeholders <- data.frame(PrivateStakeholdersGrid, PrivateRegionGrid) # Double-grid
RegionByStakeholders2 <- melt(RegionByStakeholders, id=c("Teachers.who.do.not.tutor","Teachers.who.tutor","Tutors.who.are.not.teachers","Parents...household","Students","Policymakers","Documents"))
RegionByStakeholders3 <- RegionByStakeholders2[!(RegionByStakeholders2$value=="FALSE"),]
names(RegionByStakeholders3) <- c("Non-tutor teachers","Teachers who tutor","Tutors","Parents","Students","Policymakers","Documents", "Region", "value")
RegionByStakeholders3 <- melt(RegionByStakeholders3, id=c("Region"))
RegionByStakeholders3<-RegionByStakeholders3[!(RegionByStakeholders3$value=="FALSE"),]
names(RegionByStakeholders3) <- c("Region","Stakeholders", "value")
RegionByStakeholders3<-RegionByStakeholders3[!(RegionByStakeholders3$Stakeholders=="value"),]
ggplot(RegionByStakeholders3, aes(Stakeholders))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByStakeholders3$Stakeholders, RegionByStakeholders3$Region))
```

# Stakeholders by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
StakeholdersByYear<-data.frame(Private$YearGroup, PrivateStakeholdersGrid) #Grid vs column
StakeholdersByYear2 <- melt(StakeholdersByYear, id=c("Private.YearGroup"))
StakeholdersByYear3<-StakeholdersByYear2[!(StakeholdersByYear2$value=="FALSE"),] 
names(StakeholdersByYear3) <- c("YearGroup","Stakeholders","value")
ggplot(StakeholdersByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Stakeholders)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(StakeholdersByYear3$YearGroup, StakeholdersByYear3$Stakeholders))
```

# Stakeholders by theory
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
StakeholdersByTheory <- data.frame(PrivateTheoryGrid, PrivateStakeholdersGrid) # Double-grid
StakeholdersByTheory2 <- melt(StakeholdersByTheory, id=c("Teachers.who.do.not.tutor","Teachers.who.tutor","Tutors.who.are.not.teachers","Parents...household","Students","Policymakers","Documents"))
StakeholdersByTheory3 <- StakeholdersByTheory2[!(StakeholdersByTheory2$value=="FALSE"),]
names(StakeholdersByTheory3) <- c("Non-tutor teachers","Tutors who tutor","Tutors","Parents","Students","Policymakers","Documents", "Stakeholders", "value")
StakeholdersByTheory3 <- melt(StakeholdersByTheory3, id=c("Stakeholders"))
StakeholdersByTheory3<-StakeholdersByTheory3[!(StakeholdersByTheory3$value=="FALSE"),]
names(StakeholdersByTheory3) <- c("Stakeholders","Theory", "value")
StakeholdersByTheory3<-StakeholdersByTheory3[!(StakeholdersByTheory3$Theory=="value"),]
ggplot(StakeholdersByTheory3, aes(Theory))+geom_bar()+facet_wrap(~Stakeholders)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(StakeholdersByTheory3$Stakeholders, StakeholdersByTheory3$Theory))
```

# WhatTaught by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByWhatTaught <- data.frame(PrivateWhatTaughtGrid, PrivateRegionGrid) # Double-grid
RegionByWhatTaught2 <- melt(RegionByWhatTaught, id=c("Subjects.taught.in.school","Extracurricular.activities..Dance..art..sports..music.","Both","Not.defined"))
RegionByWhatTaught3 <- RegionByWhatTaught2[!(RegionByWhatTaught2$value=="FALSE"),]
names(RegionByWhatTaught3) <- c("School subjects","Extracurriculars","Both","Not defined", "Region", "value")
RegionByWhatTaught3 <- melt(RegionByWhatTaught3, id=c("Region"))
RegionByWhatTaught3<-RegionByWhatTaught3[!(RegionByWhatTaught3$value=="FALSE"),]
names(RegionByWhatTaught3) <- c("Region","WhatTaught", "value")
RegionByWhatTaught3<-RegionByWhatTaught3[!(RegionByWhatTaught3$WhatTaught=="value"),]
ggplot(RegionByWhatTaught3, aes(WhatTaught))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByWhatTaught3$WhatTaught, RegionByWhatTaught3$Region))
```

WhatTaught by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhatTaughtByYear<-data.frame(Private$YearGroup, PrivateWhatTaughtGrid) #Grid vs column
WhatTaughtByYear2 <- melt(WhatTaughtByYear, id=c("Private.YearGroup"))
WhatTaughtByYear3<-WhatTaughtByYear2[!(WhatTaughtByYear2$value=="FALSE"),] 
names(WhatTaughtByYear3) <- c("YearGroup","WhatTaught","value")
ggplot(WhatTaughtByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~WhatTaught)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhatTaughtByYear3$YearGroup, WhatTaughtByYear3$WhatTaught))
```

# WhatTaught by theory
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhatTaughtByTheory <- data.frame(PrivateTheoryGrid, PrivateWhatTaughtGrid) # Double-grid
WhatTaughtByTheory2 <- melt(WhatTaughtByTheory, id=c("Subjects.taught.in.school","Extracurricular.activities..Dance..art..sports..music.","Both","Not.defined"))
WhatTaughtByTheory3 <- WhatTaughtByTheory2[!(WhatTaughtByTheory2$value=="FALSE"),]
names(WhatTaughtByTheory3) <- c("School subjects","Extracurriculars","Both","Not defined", "WhatTaught", "value")
WhatTaughtByTheory3 <- melt(WhatTaughtByTheory3, id=c("WhatTaught"))
WhatTaughtByTheory3<-WhatTaughtByTheory3[!(WhatTaughtByTheory3$value=="FALSE"),]
names(WhatTaughtByTheory3) <- c("WhatTaught","Theory", "value")
WhatTaughtByTheory3<-WhatTaughtByTheory3[!(WhatTaughtByTheory3$Theory=="value"),]
ggplot(WhatTaughtByTheory3, aes(Theory))+geom_bar()+facet_wrap(~WhatTaught)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhatTaughtByTheory3$WhatTaught, WhatTaughtByTheory3$Theory))
```

# WhereOccur by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByWhereOccur <- data.frame(PrivateWhereOccurGrid, PrivateRegionGrid) # Double-grid
RegionByWhereOccur2 <- melt(RegionByWhereOccur, id=c("On.school.grounds","Designated.tutoring.center.or.franchise","On.line...via.web","In.the.student.s.home","Other.outside.school..e.g..teacher.s.home..coffee.shop..library.","Not.defined"))
RegionByWhereOccur3 <- RegionByWhereOccur2[!(RegionByWhereOccur2$value=="FALSE"),]
names(RegionByWhereOccur3) <- c("On school grounds","Designated center","Web","Student's home","Outside school","Not defined", "Region", "value")
RegionByWhereOccur3 <- melt(RegionByWhereOccur3, id=c("Region"))
RegionByWhereOccur3<-RegionByWhereOccur3[!(RegionByWhereOccur3$value=="FALSE"),]
names(RegionByWhereOccur3) <- c("Region","WhereOccur", "value")
RegionByWhereOccur3<-RegionByWhereOccur3[!(RegionByWhereOccur3$WhereOccur=="value"),]
ggplot(RegionByWhereOccur3, aes(WhereOccur))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByWhereOccur3$WhereOccur, RegionByWhereOccur3$Region))
```

# WhereOccur by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhereOccurByYear<-data.frame(Private$YearGroup, PrivateWhereOccurGrid) #Grid vs column
WhereOccurByYear2 <- melt(WhereOccurByYear, id=c("Private.YearGroup"))
WhereOccurByYear3<-WhereOccurByYear2[!(WhereOccurByYear2$value=="FALSE"),] 
names(WhereOccurByYear3) <- c("YearGroup","WhereOccur","value")
ggplot(WhereOccurByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~WhereOccur)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhereOccurByYear3$YearGroup, WhereOccurByYear3$WhereOccur))
```

# WhereOccur by theory
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhereOccurByTheory <- data.frame(PrivateTheoryGrid, PrivateWhereOccurGrid) # Double-grid
WhereOccurByTheory2 <- melt(WhereOccurByTheory, id=c("On.school.grounds","Designated.tutoring.center.or.franchise","On.line...via.web","In.the.student.s.home","Other.outside.school..e.g..teacher.s.home..coffee.shop..library.","Not.defined"))
WhereOccurByTheory3 <- WhereOccurByTheory2[!(WhereOccurByTheory2$value=="FALSE"),]
names(WhereOccurByTheory3) <- c("On school grounds","Designated center","Web","Student's home","Outside school","Not defined", "WhereOccur", "value")
WhereOccurByTheory3 <- melt(WhereOccurByTheory3, id=c("WhereOccur"))
WhereOccurByTheory3<-WhereOccurByTheory3[!(WhereOccurByTheory3$value=="FALSE"),]
names(WhereOccurByTheory3) <- c("WhereOccur","Theory", "value")
WhereOccurByTheory3<-WhereOccurByTheory3[!(WhereOccurByTheory3$Theory=="value"),]
ggplot(WhereOccurByTheory3, aes(Theory))+geom_bar()+facet_wrap(~WhereOccur)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhereOccurByTheory3$WhereOccur, WhereOccurByTheory3$Theory))
```

# WhoProvides by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByWhoProvides <- data.frame(PrivateWhoProvidesGrid, PrivateRegionGrid) # Double-grid
RegionByWhoProvides2 <- melt(RegionByWhoProvides, id=c("Current.classroom.teacher","Other.K.12.teachers","Retired.teacher","University.faculty","Institution...Professional.tutor","College.student","Peer.classmate","Parent.or.family.member","Community.member...volunteer","Not.defined"))
RegionByWhoProvides3 <- RegionByWhoProvides2[!(RegionByWhoProvides2$value=="FALSE"),]
names(RegionByWhoProvides3) <- c("Current teacher", "Other k-12","Retired teacher","Univ. faculty","Professional","Col. student","Peer","Family","Community","Not defined" , "Region", "value")
RegionByWhoProvides3 <- melt(RegionByWhoProvides3, id=c("Region"))
RegionByWhoProvides3<-RegionByWhoProvides3[!(RegionByWhoProvides3$value=="FALSE"),]
names(RegionByWhoProvides3) <- c("Region","WhoProvides", "value")
RegionByWhoProvides3<-RegionByWhoProvides3[!(RegionByWhoProvides3$WhoProvides=="value"),]
ggplot(RegionByWhoProvides3, aes(WhoProvides))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByWhoProvides3$WhoProvides, RegionByWhoProvides3$Region))
```

# WhoProvides by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhoProvidesByYear<-data.frame(Private$YearGroup, PrivateWhoProvidesGrid) #Grid vs column
WhoProvidesByYear2 <- melt(WhoProvidesByYear, id=c("Private.YearGroup"))
WhoProvidesByYear3<-WhoProvidesByYear2[!(WhoProvidesByYear2$value=="FALSE"),] 
names(WhoProvidesByYear3) <- c("YearGroup","WhoProvides","value")
ggplot(WhoProvidesByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~WhoProvides)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhoProvidesByYear3$YearGroup, WhoProvidesByYear3$WhoProvides))
```

# WhoProvides by theory
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhoProvidesByTheory <- data.frame(PrivateTheoryGrid, PrivateWhoProvidesGrid) # Double-grid
WhoProvidesByTheory2 <- melt(WhoProvidesByTheory, id=c("Current.classroom.teacher","Other.K.12.teachers","Retired.teacher","University.faculty","Institution...Professional.tutor","College.student","Peer.classmate","Parent.or.family.member","Community.member...volunteer","Not.defined"))
WhoProvidesByTheory3 <- WhoProvidesByTheory2[!(WhoProvidesByTheory2$value=="FALSE"),]
names(WhoProvidesByTheory3) <- c("Current teacher", "Other k-12","Retired teacher","Univ. faculty","Professional","Col. student","Peer","Family","Community","Not defined" , "WhoProvides", "value")
WhoProvidesByTheory3 <- melt(WhoProvidesByTheory3, id=c("WhoProvides"))
WhoProvidesByTheory3<-WhoProvidesByTheory3[!(WhoProvidesByTheory3$value=="FALSE"),]
names(WhoProvidesByTheory3) <- c("WhoProvides","Theory", "value")
WhoProvidesByTheory3<-WhoProvidesByTheory3[!(WhoProvidesByTheory3$Theory=="value"),]
ggplot(WhoProvidesByTheory3, aes(Theory))+geom_bar()+facet_wrap(~WhoProvides)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhoProvidesByTheory3$WhoProvides, WhoProvidesByTheory3$Theory))
```

# DoesCharge by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByDoesCharge <- data.frame(Private$DoesCharge, PrivateRegionGrid) # single-grid
RegionByDoesCharge2 <- melt(RegionByDoesCharge, id=c("Private.DoesCharge"))
RegionByDoesCharge3 <- RegionByDoesCharge2[!(RegionByDoesCharge2$value=="FALSE"),]
names(RegionByDoesCharge3) <- c("DoesCharge","Region", "value")
RegionByDoesCharge3<-RegionByDoesCharge3[!(RegionByDoesCharge3$DoesCharge=="value"),]
ggplot(RegionByDoesCharge3, aes(DoesCharge))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByDoesCharge3$DoesCharge, RegionByDoesCharge3$Region))
```

# DoesCharge by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ggplot(Private, aes(YearGroup))+geom_bar()+facet_wrap(~DoesCharge)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(Private$YearGroup, Private$DoesCharge))
```

# DoesCharge by WhoProvides
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhoProvidesByDoesCharge <- data.frame(Private$DoesCharge, PrivateWhoProvidesGrid) # single-grid
WhoProvidesByDoesCharge2 <- melt(WhoProvidesByDoesCharge, id=c("Private.DoesCharge"))
WhoProvidesByDoesCharge3 <- WhoProvidesByDoesCharge2[!(WhoProvidesByDoesCharge2$value=="FALSE"),]
names(WhoProvidesByDoesCharge3) <- c("DoesCharge","WhoProvides", "value")
WhoProvidesByDoesCharge3<-WhoProvidesByDoesCharge3[!(WhoProvidesByDoesCharge3$DoesCharge=="value"),]
ggplot(WhoProvidesByDoesCharge3, aes(DoesCharge))+geom_bar()+facet_wrap(~WhoProvides)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhoProvidesByDoesCharge3$DoesCharge, WhoProvidesByDoesCharge3$WhoProvides))
```

# ClassSize by Region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByClassSize <- data.frame(Private$ClassSize, PrivateRegionGrid) # single-grid
RegionByClassSize2 <- melt(RegionByClassSize, id=c("Private.ClassSize"))
RegionByClassSize3 <- RegionByClassSize2[!(RegionByClassSize2$value=="FALSE"),]
names(RegionByClassSize3) <- c("ClassSize","Region", "value")
RegionByClassSize3<-RegionByClassSize3[!(RegionByClassSize3$ClassSize=="value"),]
ggplot(RegionByClassSize3, aes(ClassSize))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByClassSize3$ClassSize, RegionByClassSize3$Region))
```

# OperationSize by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByOperationSize <- data.frame(PrivateOperationSizeGrid, PrivateRegionGrid) # Double-grid
RegionByOperationSize2 <- melt(RegionByOperationSize, id=c("Individual.operator","Small.firm","Large.firm","Various"))
RegionByOperationSize3 <- RegionByOperationSize2[!(RegionByOperationSize2$value=="FALSE"),]
names(RegionByOperationSize3) <- c("Individual","Small firms","Large firm","Various" , "Region", "value")
RegionByOperationSize3 <- melt(RegionByOperationSize3, id=c("Region"))
RegionByOperationSize3<-RegionByOperationSize3[!(RegionByOperationSize3$value=="FALSE"),]
names(RegionByOperationSize3) <- c("Region","OperationSize", "value")
RegionByOperationSize3<-RegionByOperationSize3[!(RegionByOperationSize3$OperationSize=="value"),]
ggplot(RegionByOperationSize3, aes(OperationSize))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByOperationSize3$OperationSize, RegionByOperationSize3$Region))
```

# Why Taking by region
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByWhyTaking <- data.frame(PrivateWhyTakingGrid, PrivateRegionGrid) # Double-grid
RegionByWhyTaking2 <- melt(RegionByWhyTaking, id=c(
"Student.falls.behind.and.needs.extra.help","Preparation.for.exams.to.make.student.more.competitive","Make.up.for.perceived.failure.in.the.mainstream.system...school","For.cultural.reasons","To.provide.extra.enrichment.activities","Peer.pressure","Teacher.pressure","Not.stated.or.unclear"))
RegionByWhyTaking3 <- RegionByWhyTaking2[!(RegionByWhyTaking2$value=="FALSE"),]
names(RegionByWhyTaking3) <- c( "Student falls behind","Preparation for exams","Make up for perceived failure","For cultural reasons","Enrichment activities","Peer pressure","Teacher pressure","Not stated or unclear", "Region", "value")
RegionByWhyTaking3 <- melt(RegionByWhyTaking3, id=c("Region"))
RegionByWhyTaking3<-RegionByWhyTaking3[!(RegionByWhyTaking3$value=="FALSE"),]
names(RegionByWhyTaking3) <- c("Region","WhyTaking", "value")
RegionByWhyTaking3<-RegionByWhyTaking3[!(RegionByWhyTaking3$WhyTaking=="value"),]
ggplot(RegionByWhyTaking3, aes(WhyTaking))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByWhyTaking3$WhyTaking, RegionByWhyTaking3$Region))
```

# Why Taking by year group
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhyTakingByYear<-data.frame(Private$YearGroup, PrivateWhyTakingGrid) #Grid vs column
WhyTakingByYear2 <- melt(WhyTakingByYear, id=c("Private.YearGroup"))
WhyTakingByYear3<-WhyTakingByYear2[!(WhyTakingByYear2$value=="FALSE"),] 
names(WhyTakingByYear3) <- c("YearGroup","WhyTaking","value")
ggplot(WhyTakingByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~WhyTaking)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhyTakingByYear3$YearGroup, WhyTakingByYear3$WhyTaking))
```



# WhyTaking by research method
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchMethodsByWhyTaking <- data.frame(PrivateWhyTakingGrid, PrivateResearchMethodsGrid) # Double-grid
ResearchMethodsByWhyTaking2 <- melt(ResearchMethodsByWhyTaking, id=c(
"Student.falls.behind.and.needs.extra.help","Preparation.for.exams.to.make.student.more.competitive","Make.up.for.perceived.failure.in.the.mainstream.system...school","For.cultural.reasons","To.provide.extra.enrichment.activities","Peer.pressure","Teacher.pressure","Not.stated.or.unclear"))
ResearchMethodsByWhyTaking3 <- ResearchMethodsByWhyTaking2[!(ResearchMethodsByWhyTaking2$value=="FALSE"),]
names(ResearchMethodsByWhyTaking3) <- c( "Student falls behind","Preparation for exams","Make up for perceived failure","For cultural reasons","Enrichment activities","Peer pressure","Teacher pressure","Not stated or unclear", "ResearchMethods", "value")
ResearchMethodsByWhyTaking3 <- melt(ResearchMethodsByWhyTaking3, id=c("ResearchMethods"))
ResearchMethodsByWhyTaking3<-ResearchMethodsByWhyTaking3[!(ResearchMethodsByWhyTaking3$value=="FALSE"),]
names(ResearchMethodsByWhyTaking3) <- c("ResearchMethods","WhyTaking", "value")
ResearchMethodsByWhyTaking3<-ResearchMethodsByWhyTaking3[!(ResearchMethodsByWhyTaking3$WhyTaking=="value"),]
ggplot(ResearchMethodsByWhyTaking3, aes(ResearchMethods))+geom_bar()+facet_wrap(~WhyTaking)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchMethodsByWhyTaking3$WhyTaking, ResearchMethodsByWhyTaking3$ResearchMethods))
```

# WhyTaking by research approach
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
ResearchApproachByWhyTaking <- data.frame(PrivateWhyTakingGrid, PrivateResearchApproachGrid) # Double-grid
ResearchApproachByWhyTaking2 <- melt(ResearchApproachByWhyTaking, id=c(
"Student.falls.behind.and.needs.extra.help","Preparation.for.exams.to.make.student.more.competitive","Make.up.for.perceived.failure.in.the.mainstream.system...school","For.cultural.reasons","To.provide.extra.enrichment.activities","Peer.pressure","Teacher.pressure","Not.stated.or.unclear"))
ResearchApproachByWhyTaking3 <- ResearchApproachByWhyTaking2[!(ResearchApproachByWhyTaking2$value=="FALSE"),]
names(ResearchApproachByWhyTaking3) <- c( "Student falls behind","Preparation for exams","Make up for perceived failure","For cultural reasons","Enrichment activities","Peer pressure","Teacher pressure","Not stated or unclear", "ResearchApproach", "value")
ResearchApproachByWhyTaking3 <- melt(ResearchApproachByWhyTaking3, id=c("ResearchApproach"))
ResearchApproachByWhyTaking3<-ResearchApproachByWhyTaking3[!(ResearchApproachByWhyTaking3$value=="FALSE"),]
names(ResearchApproachByWhyTaking3) <- c("ResearchApproach","WhyTaking", "value")
ResearchApproachByWhyTaking3<-ResearchApproachByWhyTaking3[!(ResearchApproachByWhyTaking3$WhyTaking=="value"),]
ggplot(ResearchApproachByWhyTaking3, aes(ResearchApproach))+geom_bar()+facet_wrap(~WhyTaking)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(ResearchApproachByWhyTaking3$WhyTaking, ResearchApproachByWhyTaking3$ResearchApproach))
```

# WhyTaking by theory
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
WhyTakingByTheory <- data.frame(PrivateTheoryGrid, PrivateWhyTakingGrid) # Double-grid
WhyTakingByTheory2 <- melt(WhyTakingByTheory, id=c(
"Student.falls.behind.and.needs.extra.help","Preparation.for.exams.to.make.student.more.competitive","Make.up.for.perceived.failure.in.the.mainstream.system...school","For.cultural.reasons","To.provide.extra.enrichment.activities","Peer.pressure","Teacher.pressure","Not.stated.or.unclear"))
WhyTakingByTheory3 <- WhyTakingByTheory2[!(WhyTakingByTheory2$value=="FALSE"),]
names(WhyTakingByTheory3) <- c("Student falls behind","Preparation for exams","Make up for perceived failure","For cultural reasons","Enrichment activities","Peer pressure","Teacher pressure","Not stated or unclear", "Theory", "value")
WhyTakingByTheory3 <- melt(WhyTakingByTheory3, id=c("Theory"))
WhyTakingByTheory3<-WhyTakingByTheory3[!(WhyTakingByTheory3$value=="FALSE"),]
names(WhyTakingByTheory3) <- c("Theory", "WhyTaking","value")
WhyTakingByTheory3<-WhyTakingByTheory3[!(WhyTakingByTheory3$Theory=="value"),]
ggplot(WhyTakingByTheory3, aes(WhyTaking))+geom_bar()+facet_wrap(~Theory)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(WhyTakingByTheory3$WhyTaking, WhyTakingByTheory3$Theory))
```

# Why Taking by Framed
### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
FramedByWhyTaking <- data.frame(PrivateWhyTakingGrid, PrivateFramedGrid) # Double-grid
FramedByWhyTaking2 <- melt(FramedByWhyTaking, id=c(
"Student.falls.behind.and.needs.extra.help","Preparation.for.exams.to.make.student.more.competitive","Make.up.for.perceived.failure.in.the.mainstream.system...school","For.cultural.reasons","To.provide.extra.enrichment.activities","Peer.pressure","Teacher.pressure","Not.stated.or.unclear"))
FramedByWhyTaking3 <- FramedByWhyTaking2[!(FramedByWhyTaking2$value=="FALSE"),]
names(FramedByWhyTaking3) <- c( "Student falls behind","Preparation for exams","Make up for perceived failure","For cultural reasons","Enrichment activities","Peer pressure","Teacher pressure","Not stated or unclear", "Framed", "value")
FramedByWhyTaking3 <- melt(FramedByWhyTaking3, id=c("Framed"))
FramedByWhyTaking3<-FramedByWhyTaking3[!(FramedByWhyTaking3$value=="FALSE"),]
names(FramedByWhyTaking3) <- c("Framed","WhyTaking", "value")
FramedByWhyTaking3<-FramedByWhyTaking3[!(FramedByWhyTaking3$WhyTaking=="value"),]
ggplot(FramedByWhyTaking3, aes(WhyTaking))+geom_bar()+facet_wrap(~Framed)+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(FramedByWhyTaking3$Framed, FramedByWhyTaking3$WhyTaking))
```