---
title: "Relationships"
output:
  html_document:
    keep_md: yes
    toc: true
  pdf_document: default
---


```{r, results="asis", echo=FALSE, message=FALSE}
source('../RCode/Download and Clean PT Data.R')
source('../RCode/PT Analysis.R')
```

# Region by years (grouped)

## _Region by year group_ for all entries in the database:

### Graphs for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByYear<-data.frame(Private$YearGroup, PrivateRegionGrid)
RegionByYear2 <- melt(RegionByYear, id=c("Private.YearGroup"))
RegionByYear3<-RegionByYear2[!(RegionByYear2$value=="FALSE"),]
names(RegionByYear3) <- c("YearGroup","Region","value")
ggplot(RegionByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Counts for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByYear3$YearGroup, RegionByYear3$Region))
```

### Percentages for all entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(prop.table(table(RegionByYear3$YearGroup, RegionByYear3$Region)))
```

## _Region by year group_ for all Asian-region entries in the database:

### Graphs for all Asian-region entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByYear<-data.frame(AllAsia$YearGroup, AllAsiaRegionGrid)
RegionByYear2 <- melt(RegionByYear, id=c("AllAsia.YearGroup"))
RegionByYear3<-RegionByYear2[!(RegionByYear2$value=="FALSE"),]
names(RegionByYear3) <- c("YearGroup","Region","value")
ggplot(RegionByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Counts for all Asian-region entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByYear3$YearGroup, RegionByYear3$Region))
```

### Percentages for all Asian-region entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(prop.table(table(RegionByYear3$YearGroup, RegionByYear3$Region)))
```

## _Region by year group_ for all Chinese-language entries in the database:

### Graphs for all Chinese-language entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByYear<-data.frame(AllChinese$YearGroup, AllChineseRegionGrid)
RegionByYear2 <- melt(RegionByYear, id=c("AllChinese.YearGroup"))
RegionByYear3<-RegionByYear2[!(RegionByYear2$value=="FALSE"),]
names(RegionByYear3) <- c("YearGroup","Region","value")
ggplot(RegionByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Counts for all Chinese-language entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByYear3$YearGroup, RegionByYear3$Region))
```

### Percentages for all Chinese-language entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(prop.table(table(RegionByYear3$YearGroup, RegionByYear3$Region)))
```

## _Region by year group_ for all English-language entries in the database:

### Graphs for all English-language entries
```{r, results="asis", echo=FALSE, message=FALSE}
RegionByYear<-data.frame(AllEnglish$YearGroup, AllEnglishRegionGrid)
RegionByYear2 <- melt(RegionByYear, id=c("AllEnglish.YearGroup"))
RegionByYear3<-RegionByYear2[!(RegionByYear2$value=="FALSE"),]
names(RegionByYear3) <- c("YearGroup","Region","value")
ggplot(RegionByYear3, aes(YearGroup))+geom_bar()+facet_wrap(~Region)+theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

### Counts for all English-language entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(table(RegionByYear3$YearGroup, RegionByYear3$Region))
```

### Percentages for all English-language entries
```{r, results="asis", echo=FALSE, message=FALSE}
kable(prop.table(table(RegionByYear3$YearGroup, RegionByYear3$Region)))
```